The supernova-regulated ISM - III. Magnetic fields in the multi-phase gas

### 2015-03-04 field_lines/mhdruns.tex
update test

  The total volume probability distributions for gas number density $n$, 
  temperature $T$ and thermal pressure $p$ are displayed in Fig.~\ref{fig:pdfm}
  from Models~$\Ompa$ (black, solid) and $\Omph$ (blue, dashed). 
%  Note that Model~$\Omph$ includes the correction to the SN distribution,
%  which stabilises the disc against unphysical cyclic oscillations, although
%  it is still subject to natural random vertical fluctuations.
%  Hence the mean density in the SN active region remains consistently higher
%  than in Model~\Op.
%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_rpdf.png}
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_tpdf.png}
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_ppdf.png}
    \caption[Total volume probability distributions for Model~$\Ompa$ and $\Omph$]{
  Volume weighted probability distributions of gas number
  density~{\textbf{(a)}}, temperature~{\textbf{(b)}} and thermal
  pressure~{\textbf{(c)}} for  models {$\Omph$} (black, solid) and
  {$\Ompa$} (blue, dashed) for the total numerical domain $|z|\le1.12\kpc$.
    \label{fig:pdfm}}
  \end{figure}
%-----------------------------------------------------------------------------
  A three phase temperature distribution is visible for Model~$\Omph$ (HD)
  model in Fig.~\ref{fig:pdfm}b, while less apparent for Model~$\Ompa$ (MHD),
  with a significantly narrower range of temperatures.
  The bulk of the density distributions (a) are quite similar between the 
  HD and MHD model, except that the high densities are not as well resolved in
  the MHD model.
  The thermal pressure distributions are very similar, but with the HD modal
  pressure approximately one third the MHD modal pressure. 
  \footnote{FAG: I think these plots are averages of several snapshots in the 
  kinematic dynamo -- need to check -- while the analysis elsewhere is on the 
  saturated field}
  Even with a relatively weak magnetic field, there is significantly increased
  stiffness to the ISM, which restricts transport of the hot gas away from the
  disk (FAG: Kompaneets?), and may also act as a break on the supersonic
  flows, reducing the material collected in the snowplough phase of the SN and
  hence less cold gas resolved in the model (FAG: cite?)
%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth]{fig/zrhom.png}
  \includegraphics[width=0.9\columnwidth]{fig/zrppm.png}
    \caption[Horizontal averages of $n$ and $P$ for Model~$\Ompa$ and $\Omph$]{
  Horizontal averages of gas number density, $\mean{n}(z)$ {\textbf{(a)}}, and
  total pressure, $\mean{P}(z)$ {\textbf{(b)}}, for Model~{$\Ompa$} (solid,
  black), and Model~{$\Omph$} (dashed, blue). 
  Each are time-averaged using eleven snapshots respectively, spanning 
  100\Myr.
  The vertical lines indicate standard deviation within each horizontal slice.
  The thermal $\mean{p}(z)$ (dotted) and ram $\mean{p}\turb(z)$ (fine dashed)
  pressures are also plotted {\textbf{(b)}}.
%  For Model~{\OpH} the magnetic pressure $\mean{p}_B$ is also plotted (fine, 
%  dash-3dotted).
    \label{fig:zrhom}
            }
  \end{figure}
%-----------------------------------------------------------------------------

>>>>

  The total volume probability distributions for gas number density $n$, 
  temperature $T$ and thermal pressure $p$ are displayed in Fig.~\ref{fig:pdfm}
  from Models~$\Ompa$ (black, solid) and $\Omph$ (blue, dashed). 
%  Note that Model~$\Omph$ includes the correction to the SN distribution,
%  which stabilises the disc against unphysical cyclic oscillations, although
%  it is still subject to natural random vertical fluctuations.
%  Hence the mean density in the SN active region remains consistently higher
%  than in Model~\Op.
%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_rpdf.png}
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_tpdf.png}
  \includegraphics[width=0.9\columnwidth,clip=true,trim=0 0 0 9mm]{fig/o1pr_ppdf.png}
    \caption[Total volume probability distributions for Model~$\Ompa$ and $\Omph$]{
  Volume weighted probability distributions of gas number
  density~{\textbf{(a)}}, temperature~{\textbf{(b)}} and thermal
  pressure~{\textbf{(c)}} for  models {$\Omph$} (black, solid) and
  {$\Ompa$} (blue, dashed) for the total numerical domain $|z|\le1.12\kpc$.
    \label{fig:pdfm}}
  \end{figure}
%-----------------------------------------------------------------------------
  A three phase temperature distribution is visible for Model~$\Omph$ (HD)
  model in Fig.~\ref{fig:pdfm}b, while less apparent for Model~$\Ompa$ (MHD),
  with a significantly narrower range of temperatures.
  The bulk of the density distributions (a) are quite similar between the 
  HD and MHD model, except that the high densities are not as well resolved in
  the MHD model.
  The thermal pressure distributions are very similar, but with the HD modal
  pressure approximately one third the MHD modal pressure. 
  \footnote{FAG: I think these plots are averages of several snapshots in the 
  kinematic dynamo -- need to check -- while the analysis elsewhere is on the 
  saturated field}
  Even with a relatively weak magnetic field, there is significantly increased
  stiffness to the ISM, which restricts transport of the hot gas away from the
  disk \citep{Tomisaka98}, and may also act as a break on the supersonic
  flows, reducing the material collected in the snowplough phase of the SN and
  hence less cold gas resolved in the model \citep{Avillez04}
%-----------------------------------------------------------------------------
  \begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth]{fig/zrhom.png}
  \includegraphics[width=0.9\columnwidth]{fig/zrppm.png}
    \caption[Horizontal averages of $n$ and $P$ for Model~$\Ompa$ and $\Omph$]{
  Horizontal averages of gas number density, $\mean{n}(z)$ {\textbf{(a)}}, and
  total pressure, $\mean{P}(z)$ {\textbf{(b)}}, for Model~{$\Ompa$} (solid,
  black), and Model~{$\Omph$} (dashed, blue). 
  Each are time-averaged using eleven snapshots respectively, spanning 
  100\Myr.
  The vertical lines indicate standard deviation within each horizontal slice.
  The thermal $\mean{p}(z)$ (dotted) and ram $\mean{p}\turb(z)$ (fine dashed)
  pressures are also plotted {\textbf{(b)}}.
%  For Model~{\OpH} the magnetic pressure $\mean{p}_B$ is also plotted (fine, 
%  dash-3dotted).
    \label{fig:zrhom}
            }
  \end{figure}
%-----------------------------------------------------------------------------
